---
title: "Introductory Vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


Here is an illustration of how to use these functions to your advantage. 


## Generate

Start by generating some data for a linear regression:
```{r Generate, eval = T}
library(R2Word)
N = 100 
number.groups <- 2
number.timepoints <- 1
set.seed(3042021)

dat <- data.frame('USUBJID' = rep(paste0('Subject_', formatC(1:N, width = 4, flag = '0')), length.out= N*number.timepoints),
                  'Group' = rep(paste0('Group_', 1:number.groups), length.out = N*number.timepoints),
                  'Y_comp' = rep(NA, N*number.timepoints), 
                  'Time' = rep(paste0('Time_', 1:number.timepoints), each = N),
                   stringsAsFactors=F)
    
        
# Design Matrix
X <- model.matrix( ~ Group , data = dat) 

# Parameters:
Beta <- matrix(0, nrow = ncol(X), dimnames=list(colnames(X), 'param'))
Beta[] <- c(0.2, 1)
sigma2 <- 9 
    
# Generate Data
XB <- X %*% Beta
dat$XB <- as.vector(XB)
error <- rnorm(n = N, mean = 0, sd = sqrt(sigma2))
dat$Y <- dat$XB + error
```


## Fit Model

Next, fit a linear regression model to the data. 

```{r Fit, eval = T}
mod <-lm(Y ~ Group, data = dat)
```


## Output Results

 Now that we have fit the model, we want to move quickly to create output. There are R packages that allow us to create output from fitted models. However, the function we will use here is very simple and clean, and allows us to output whatever we want. For example, with a few single steps we can dump this dataframe as MS Word output:
 
```{r dir, echo = F, eval = T}
print.to.this.directory = "C:/Users/ciaconangelo/Documents"
```

```{r dump}
out <- coef(summary(mod))
out <- cbind.data.frame('Predictor' = c('Intercept', 'Group 2'), out)
# Now we have the variable names as a column in the dataframe

dump_df_mat_to_file(out = out, 
                    decimals = c(1, 2, 2, 3), 
                    table.title = 'OLS Output - Vignette Illustration', 
                    table.footnote = '**All data simulated',
                    file.name = 'OLS_output_vignette', 
                    print.dir = print.to.this.directory)
```


Okay now let's try out the `create_tables()` function. We can use that to create frequency tables. 

```{r crosstabs rows}
# Generate ordinal data:
dat$Y_ord <- sample(x = c(0, 1, 2, 3), size = N, replace = T)
out <- xtabs( ~ Group + Y_ord, data = dat)

# Row sums
out <- create_tables(out, prop.table.margin = 1, add.margins = 1)
out <- cbind.data.frame('Group' = rownames(out), out)

dump_df_mat_to_file(out = out, 
                    table.title = 'Cross-tabs, N(%), row sums - Vignette Illustration', 
                    table.footnote = '**All data simulated',
                    file.name = 'cross_tabs_row_vignette', 
                    print.dir = print.to.this.directory)
```

We can also use column sums:


```{r crosstabs cols}
# Column sums
out <- xtabs( ~ Group + Y_ord, data = dat)

# Now just a few steps between the cross-tabs and a table in a MS Word doc
out <- create_tables(out, prop.table.margin = 2, add.margins = 2)
out <- cbind.data.frame('Group' = rownames(out), out)

# Dump output
dump_df_mat_to_file(out = out, 
                    table.title = 'Cross-tabs, N(%), col sums - Vignette Illustration', 
                    table.footnote = '**All data simulated',
                    file.name = 'cross_tabs_col_vignette', 
                    print.dir = print.to.this.directory)
```

As you can see, with just a couple of extra lines of code, you can move from the output of an R function like `lm()` or `xtabs` to a simple, clean MS Word doc. The `flextable` package is very flexible but for our purposes we just want a standard, easy way to dump our matrix or dataframe out to a MS Word file. 
