---
title: "Misc Code Library"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Misc_Functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This is a collection of miscellaneous functions and code that I have found useful over the years. The context of their application varies widely. Please send me code that is applicable here that you want your teammates to have on-hand. Note that the king of R libraries with miscellaneous functions is, of course, the `Hmisc` R package, from Frank Harrell. 




## Compute Statistical Indices from Rodriguez & Reise 2016


A function to compute the Explained Common Variance (ECV) and the omega, and the omegaH values in IRT models. To be used in conjunction with the `mirt` R package.


```{r ecvt, eval = F}

# Note: mod is an object from the mirt R package

ecv.and.omega.and.H <- function(mod){
  mat <- summary(mod, verbose = F)
#ECV
out <- apply(mat$rotF, 2, function(x) sum(x^2))
ecv <- out[1] / sum(out)

#omega
out.G <- sum(mat$rotF[,1])^2
if(ncol(mat$rotF) > 1){out.S1 <- sum(  apply(mat$rotF[ , 2:ncol(mat$rotF), drop = F], 2, function(x) sum(x)^2 )  ) }else{out.S1 = 0}
out.h2 <- sum(1-mat$h2)    
omega <- (out.G + out.S1)/(out.G + out.S1 + out.h2)

#omega h
omega.h <- out.G/(out.G + out.S1 + out.h2)

# H - construct reliability or construct replicability
num = (mat$rotF[ , 1])^2
denom = 1 - (mat$rotF[ , 1])^2
H = 1 / (  1 + 1/(sum(num/denom))  )

mat.out <- matrix(NA, 1, 5)
mat.out[1, ] <- c(ecv, H, omega, omega.h, omega.h/omega)
colnames(mat.out) <- c('ECV', 'H', 'omega', 'omega.h', 'ratio')
return(mat.out)
}
```


## Create Data Dictionary from SAS files


```{r data_dic, eval = F}

library(haven)
file.names <- list.files(path = "C:/Users/...")
file.names <- file.names[file.names != 'formats.sas7bcat']

data.dic <- list() 


for(i in file.names){
  
  dat <- read_sas(data_file = paste0(i))
  tmp <- cbind(lapply(dat, function(x) attributes(x)$label)) # DESCRIPTIONS OF VARIABLES
  data.dic[[i]] <- tmp
  
}
    
# Seared data:
file.names <- list.files(path = "C:/Users/...")
for(i in file.names){
  
  dat <- read_sas(data_file = paste0(i))
  tmp <- cbind(lapply(dat, function(x) attributes(x)$label)) # DESCRIPTIONS OF VARIABLES
  data.dic[[i]] <- tmp
  
}


# Search the labels/attributes collected in the data dictionary
lapply(data.dic, function(x) which(grepl('Born', x, ignore.case = T)))
  unlist(lapply(data.dic, function(x) which(grepl('Born', x, ignore.case = T))))

# Search the variable names collected in the data dictionary
lapply(data.dic, function(x) which(grepl('dob', row.names(x), ignore.case = T)))
  unlist(lapply(data.dic, function(x) which(grepl('dob', row.names(x), ignore.case = T))))

# Search labels/attributes in a particular dataset:
grep('Taf', cbind(lapply(sad2, function(x) attributes(x)$label)), ignore.case = T, value = T) 

# Search the variables names in a particular dataset:
colnames(sad2)[grep('Taf', cbind(lapply(sad2, function(x) attributes(x)$label)), ignore.case = T, value = F)]



```



## Capitalize the first letter of every word in a string

https://stat.ethz.ch/R-manual/R-devel/library/base/html/chartr.html
```{r cap, eval = F}

capwords <- function(s, strict = FALSE) {
    cap <- function(s) paste(toupper(substring(s, 1, 1)),
                  {s <- substring(s, 2); if(strict) tolower(s) else s},
                             sep = "", collapse = " " )
    sapply(strsplit(s, split = " "), cap, USE.NAMES = !is.null(names(s)))
}

```


# RMSEA Power Analysis

## RMSEA Theoretical Power Computation

This function computes the theoretical power - this is the heart of the methodological advancement. 

```{r rmsea1, eval = F}
theoretical.power <- function(type, alpha, nlow, nhigh, step, RMSEA0, RMSEA1, number.of.items, categories.per.item){
  
  P = number.of.items
  K = categories.per.item

  
  if(type == 'C2'){

    M1 = P*(K-1) 
    M2 = ncol(combn(P, 2)) 
    Q = 1*P + P*(K-1) 
    DF = M1 + M2 - Q 

  }
  
  if(type == 'M2*'){

    M1 = P
    M2 = ncol(combn(P, 2))
    Q = 1*P + P*(K-1) 
    DF = M1 + M2 - Q   
    
    
  }
  
  if(!(type %in% c('C2', 'M2*'))) { print('What statistic do you want me to fit, dude? Either C2 or M2*, pick one') }
  
  
  Power <- vector()
  for(N in seq(nlow, nhigh, by = step)){

    NCP0 = (N-1)*DF*(RMSEA0^2)
    NCP1 = (N-1)*DF*(RMSEA1^2)

    CVAL = qchisq(1 - alpha, DF, NCP0)
    tmp = 1 - pchisq(CVAL, DF, NCP1)
    Power <- rbind(Power, tmp)

  }
  
  out <- cbind(seq(nlow, nhigh, by = step), DF, Power)
  colnames(out) <- c('Sample Size', 'DF', 'Power')  
  return(out)
  
}#end theoretical power function
  
  


```

## RMSEA Power Estimation 
Based on the research we presented at conferences. There's a manuscript somewhere. 

```{r rmsea, eval = F}
# Close fit:
RMSEA0 <- 0.00  
RMSEA1 <- 0.05
# Not-close fit:
RMSEA0 <- 0.05
RMSEA1 <- 0.10
alpha <- 0.05
nlow <- 25
nhigh <- 400
step <- 25
test.lengths <- c(6, 11, 13)
categories.per.item <- 5
type = 'C2'
print.digits = "%.2f"
##########


estimate_power <- function(type = NULL,  alpha = 0.05, nlow = 25, nhigh = 500, step = 25, 
                                RMSEA0 = NULL, RMSEA1 = NULL, 
                                test.lengths = NULL, categories.per.item = NULL, 
                                print.digits = "%.2f", 
                                output.directory = NULL){
     
# Check inputs:  
  if (RMSEA0 == 0 & RMSEA1 > 0) {
    fit <- 'Test of Exact Fit'
    print(fit)
  } else {
    if (RMSEA0 > 0 & RMSEA1 > RMSEA0) {
      fit <- 'Test of Not-Close Fit'
      print(fit)
    } else { break('What kind of test is this? Check your RMSEA!')}}
# end check of inputs    
  
   out <- vector()
   
for(j in test.lengths) {

      power_theoretical <- theoretical.power(type = type, alpha = alpha, nlow=nlow, nhigh=nhigh, step=step, 
                                                RMSEA0 = RMSEA0, RMSEA1 = RMSEA1 , 
                                                number.of.items = j, categories.per.item = categories.per.item)

      out <- cbind(out, power_theoretical[ , 'Power'])

}
      
# organize output:
colnames(out) <- paste0( 'Items_', test.lengths)
est.power <- data.frame('Sample_Size' = power_theoretical[ , 'Sample Size'], out)
rownames(est.power) <- paste0(type, ' ', fit, ' ', est.power$Sample_Size)


# PLOT  
png(file = paste0('test_RMSEA Power Analysis ', type, ' ', fit, '.png'))

    tests <- paste0('Items_', test.lengths)
    test.colors <- seq(1, length(tests))
    par(mar=c(5,4,2,2)+0.1)
    plot( seq(nlow,nhigh, by = step), y = NULL, ylim = c(0,1), xaxt = 'n', xlim = c(0, nhigh), 
              xlab = 'Sample Size', ylab = 'Power')
    axis(side = 1, at = seq(0, nhigh, by = 50))
    i = 1

  for(plot.test in tests){
  
      y.axis <- est.power[ , plot.test]
      points( seq(nlow,nhigh, by = step), y = y.axis, ylim = c(0,1), xaxt = 'n', xlim = c(0, nhigh), 
                xlab = 'Sample Size', ylab = 'Power', lwd = 2, lty = 1, col = test.colors[i])
      lines( seq(nlow,nhigh, by = step), y.axis, lwd = 2, col = test.colors[i])
      i = i + 1
    }

    
    legend('bottomright', title = paste0(type, ' ', fit ), legend = tests, 
              col=test.colors, lty=1, lwd = 2, cex = 1)
    abline(h = .8, lty = 2) # put a dotted line at power = .80

dev.off() # End plot



# Output Tables:
out <- est.power
out[  , grep('Items', colnames(out))] <- 
            apply(out[  , grep('Items', colnames(out)), drop = F], 2,  function(x)  sprintf(fmt = print.digits, x))

colnames(out) <- c('Sample Size', paste0(test.lengths, ' Items'))
if(is.null(output.directory)) { 
  output.directory <- 'R1 Code Library/power_curves.doc'
}

return(est.power)

} # end estimate_power()

estimate_power(type = 'C2', RMSEA0 = 0.05, RMSEA1 = 0.08, test.lengths = test.lengths, categories.per.item = 5) 



```


## Write out rtf tables

Example of how to write out R tables to MS Word .doc files

```{r rtf, eval = F}

library(rtf)
rtf<-RTF("C:/Users/.../demo_table.doc",  width=8.5, height=11, font.size=14, omi=c(1,1,1,1))
addTable(rtf,  out, font.size= 12, row.names=F, NA.string="", header.col.justify = 'C', col.justify='C', col.widths=   c(rep(1, ncol(out))))
done(rtf)

```


## Create tables with MMRM output using `nlme` R package output


```{r mmrm_table, eval = F}

mmrm_table <- function(mod1.delta, 
                       add.baseline.row = F, 
                       n = NULL, 
                       decimal.est = 2, decimal.p = 3, 
                       var.names = NULL, 
                       output.flextable = F){
  

  library(nlme)
  out <- intervals(mod1.delta)
  out <- as.data.frame(out$coef)
  out$label <- rownames(out)
  tmp <- as.data.frame(summary(mod1.delta)$tTable) 
  out$p <- tmp$p
  out$lower <- sprintf(paste0('%.', decimal.est, 'f'),  out$lower)
  out$upper <- sprintf(paste0('%.', decimal.est, 'f'),  out$upper)
  out$est  <- sprintf(paste0('%.', decimal.est, 'f'),  out$est)
  out$p  <- sprintf(paste0('%.', decimal.p, 'f'),  out$p)
  out$conf.int <- paste0('(', out$lower, ', ', out$upper, ')')
  
  out <- out[ , c('label', 'est', 'conf.int', 'p')]
  rownames(out) <- NULL
  colnames(out) <- c('Variable', 'Estimate', 'Confidence Interval', 'P-value')
  
  
  # Want to add this row for baseline? 
  if(add.baseline.row != F) {
    
    out <- rbind(
      rep('-', ncol(out)), 
      out)
    
  }

  # Add the sample sizes? have to pass them:
  if(!is.null(n)) { 
    
    out[ , 'n'] <- n
    out <- out[ , c('Variable', 'n' , 'Estimate', 'Confidence Interval', 'P-value')]
    
  }
  
  # If you want to write the names of the variables, this is easiest way:
  if(!is.null(var.names)) {
    out$Variable <- var.names
  }
  
  
  if(output.flextable == T){
    
    library(flextable)
    library(officer)

    myft <- flextable(out)
    # Set the font to Arial:
    myft <- font(myft, fontname = "Arial", part = 'all')
    # Make header bold:
    myft <- bold(myft, part = 'header')
    # Align it
    myft <- autofit(myft)
    # Center:
    myft <- align(myft, align = "center", part = "all" )
    
    out <- myft
  }
  

  
  return(out)
  
  
} # end function

  

```


## Create tables with MMRM marginal means using `emmeans` R package output

``` {r emmeans, eval = F}
#  
 decimal.est = 2; decimal.p = 3; variables <- c('visit', 'SUBGRP_CRS'); variable.labels <- c('Visit', 'Subgroup')
 #decimal.est = 2; decimal.p = 3; variables <- NULL; variable.labels <- NULL

emmeans_table <- function(mod.emms, variables = NULL, variable.labels = NULL, var.names = NULL,
                       add.baseline.row = F, 
                       n = NULL, 
                       decimal.est = 2, decimal.p = 3, 
                       output.flextable = F){
  

  library(nlme)
  library(emmeans)
  out <- as.data.frame(confint(mod.emms))
  out$p <- test(mod.emms)$p

  out$lower <- sprintf(paste0('%.', decimal.est, 'f'),  out$lower.CL)
  out$upper <- sprintf(paste0('%.', decimal.est, 'f'),  out$upper.CL)
  out$est  <- sprintf(paste0('%.', decimal.est, 'f'),  out$emmean)
  out$p  <- sprintf(paste0('%.', decimal.p, 'f'),  out$p)
  out$conf.int <- paste0('(', out$lower, ', ', out$upper, ')')
  out[ , sapply(out, is.factor)] <- as.character(out[ , sapply(out, is.factor)])

  out <- out[ , c(variables, 'est', 'conf.int', 'p')]
  rownames(out) <- NULL
  out[ , sapply(out, is.factor)] <- as.character(out[ , sapply(out, is.factor)])
  colnames(out) <- c(variable.labels, 'Estimate', 'Confidence Interval', 'P-value')

  # Want to add this row for baseline? 
  if(add.baseline.row != F) {
    
    out <- rbind(
      rep('-', ncol(out)), 
      out[out[ , 'Subgroup'] == 0, ],
      rep('-', ncol(out)), 
      out[out[ , 'Subgroup'] == 1, ]      
      )
    
  }

  # Add the sample sizes? have to pass them:
  if(!is.null(n)) { 
    
    out$n <- n
    out <- out[ , c(variable.labels, 'n' , 'Estimate', 'Confidence Interval', 'P-value')]
    
  }
  
  # If you want to write the names of the variables, this is easiest way:
  if(!is.null(var.names)) {
    out[, variables] <- var.names
  }
  
  
  if(output.flextable == T){
    
    library(flextable)
    library(officer)

    myft <- flextable(out)
    # Set the font to Arial:
    myft <- font(myft, fontname = "Arial", part = 'all')
    # Make header bold:
    myft <- bold(myft, part = 'header')
    # Align it
    myft <- autofit(myft)
    # Center:
    myft <- align(myft, align = "center", part = "all" )
    
    out <- myft
  }
  

  
  return(out)
  
  
} # end function

```


## Site Outliers - Cook's D

```{r outliers, eval = F}

library(stringr)
library(lme4)
library(influence.ME)


# Random Effects
# Plot residuals
mod.random <- glmer(TWOHR_PAIN_FREED ~ TXA +  (1|SITEID), nAGQ = 9, family = 'binomial', data = dat)


############
# SITE LEVEL
# Criteria  - a site needs to be twice as influential as other sites to be considered for exclusion


dfbetas.mm.obs <- influence.ME:::influence(mod.random, group = 'SITEID')


number.sites <- length(unique(dat$SITEID))



 CooksD <- vector()

for(i in 1:number.sites){

    CooksD <- c(CooksD, (dfbetas.mm.obs$or.fixed[ , 'TXA'] - dfbetas.mm.obs$alt.fixed[i, 'TXA']) %*%
                            solve(dfbetas.mm.obs$or.vcov)[ 'TXA', 'TXA'] %*%
                              t(dfbetas.mm.obs$or.fixed[ , 'TXA'] - dfbetas.mm.obs$alt.fixed[i, 'TXA']) )

    
    
}


 
names(CooksD) <- unique(dat$SITEID)
sort(CooksD, decreasing = T)[1] >  2*sort(CooksD, decreasing = T)[2]

# Plot for slides
    plot(CooksD, ylab = paste0('Cook', "'",'s D'), ylim = c(0, 1), xlab = 'Site', main = paste0('Site Outliers') )
    points(  which(CooksD > 0.5)    , CooksD[which(CooksD > 0.5)], col = 'red', pch = 19 )
    text(which(CooksD > 0.5)+3, CooksD[which(CooksD > 0.5)], '609')




covratio   <- vector()

for(i in 1:number.sites){

covratio <- c(covratio,
                  dfbetas.mm.obs$alt.vcov[[i]][ 'TXA', 'TXA'] /
                    dfbetas.mm.obs$or.vcov[ 'TXA', 'TXA']
)
   
}




sort(covratio, decreasing = T)[1] > 2*sort(covratio, decreasing = T)[2]

names(covratio) <- unique(dat$SITEID)
all( names(covratio) == row.names(dfbetas.mm.obs$alt.test) )


# Plot for slides
    plot(covratio, ylab = 'Covratio', xlab = 'Site', ylim = c(1, 1.10), main = paste0('Site Outliers') )
    
    #Color the biggest outlier:
    points(  which.max(covratio)    , covratio[which.max(covratio)], col = 'red', pch = 19 )
        text(which.max(covratio) + 3, covratio[which.max(covratio)], names(covratio)[which.max(covratio)])

        


```


## Multiplot Function

This is pretty old, so it's not clear how it works in relation to the gridArrange function. 

```{r plots, eval = F}
multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  library(grid)
  
  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)
  
  numPlots = length(plots)
  
  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    # Make the panel
    # ncol: Number of columns of plots
    # nrow: Number of rows needed, calculated from # of cols
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                     ncol = cols, nrow = ceiling(numPlots/cols))
  }
  
  if (numPlots==1) {
    print(plots[[1]])
    
  } else {
    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))
    
    # Make each plot, in the correct location
    for (i in 1:numPlots) {
      # Get the i,j matrix positions of the regions that contain this subplot
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))
      
      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col), na.print = " ")
    }
  }
}

```

## Plot IRT Test Info & Item Info Curves (ICC)

used in conjunction with the `mirt` R package

```{r irt_plot_1, eval = F}


# Plots
source("C:/Users/ciaconangelo/Documents/Code Library/multiplot function.R")

# Find the test information (for a bifactor)
# Number of items:
number.items = 9


test.info <- vector()
for(it in 1:number.items){
  extr <- extract.item(mod, item = it)
  tmp <- iteminfo(extr,Theta = cbind(seq(-3, 3, length.out = 120), 0), degrees = c(0, 90))  #) > max.info){ max.info <- max(iteminfo(extr, Theta = cbind(seq(-3, 3, length.out = 120), 0), degrees = c(0, 90)))}
  test.info <- cbind(test.info, tmp)
}
test.info <- rowSums(test.info)
plot(test.info)
df1 <- data.frame('theta' = seq(-3, 3, length.out = 120), 'info'= test.info)


# for DIF, you have multiplegroups, do the info for a single group:
#  extract.item(mod, item = it, group = 1 )
# Pull it group at a time




#Find the maximum information:
max.info <- 0
for(it in 1:number.items){
  extr <- extract.item(mod, item = it)
  if(max(iteminfo(extr,Theta = cbind(seq(-3, 3, length.out = 120), 0), degrees = c(0, 90))) > max.info){ max.info <- max(iteminfo(extr, Theta = cbind(seq(-3, 3, length.out = 120), 0), degrees = c(0, 90)))}
}

for(it in 1:number.items){
  extr <- extract.item(mod, item = it)
  info <- iteminfo(extr, Theta = cbind(seq(-3, 3, length.out = 120), 0), degrees = c(0, 90))
  df1 <- data.frame('theta' = seq(-3, 3, length.out = 120), 'info'=info)
  plot.info <-   ggplot(data = df1, aes(x = theta, y = info)) +
    geom_line()+ 
    coord_cartesian(ylim = c(0, max.info), xlim = c(-3, 3)) +
    labs(title = paste0(colnames(dat)[it]), x = expression(theta), y = 'Information') +
    theme(plot.title = element_text(hjust = 0.5)) 
  
  trace <- probtrace(extr, Theta = cbind(seq(-2, 2, length.out = 120), 0))
  df2 <- melt(trace)
  df2$theta <- seq(-3, 3, length.out = 120)
  plot.icc <- ggplot(data=df2,
                     aes(x=theta, y=value, colour=Var2)) +
    geom_line() +
    coord_cartesian(ylim = c(0,1)) +
    labs(title = paste0(colnames(dat)[it]), x = expression(theta), y = 'Probability', color = 'Category') +
    theme(plot.title = element_text(hjust = 0.5)) +
    theme(legend.position=c(.5, .95), legend.direction = 'horizontal') +
    scale_color_manual(labels = c(paste0(min(dat[,it], na.rm = T):max(dat[,it], na.rm = T))), values = c(paste0(min(dat[,it], na.rm = T):max(dat[,it], na.rm =T) + 1))) 

  
  multiplot(plot.info, plot.icc, cols = 2)
  
}


```



## Multidimensional IRT plots

Multiple Dimension plots of Test info, Item info, and ICC

```{r irt_plots2, eval = F}

# Call your mirt model 'mod'
item.responses <- df.cc.ds[ , grep('FAB', colnames(df) )[-17]]
number.items = 16
theta.grid <- matrix(seq(-3, 3, length.out = 120), 120, ncol = 2)
item.labels <- item.symptoms
item.range <- apply(item.responses, 2, range, na.rm = T)
item.range <- apply(item.range, 2, function(x) seq(x[1], x[2]) )
source("C:/Users/ciaconangelo/Documents/R1 Code Library/multiplot function.R")


test.info <- vector()
for(it in c(1:8) ){
  extr <- extract.item(mod, item = it)  
  tmp <- iteminfo(extr,Theta = theta.grid, degrees = c(0, 90)) # First dimension only!
  test.info <- cbind(test.info, tmp)
}
test.info <- rowSums(test.info)


test.info2 <- vector()
for(it in c(5, 9:16) ){
  extr <- extract.item(mod, item = it)  
  tmp <- iteminfo(extr,Theta = theta.grid, degrees = c(90, 0))  #Second dimension only! 
  #Phil: "I think you want degrees = c(90, 0, 0). That will drop the first dimension and include all of the 2nd and 3rd."
  test.info2 <- cbind(test.info2, tmp)
}
test.info2 <- rowSums(test.info2)
df.test <- data.frame('theta' = theta.grid[,1], 'info1'= test.info, 'info2' = test.info2)

plot(df.test$theta, df.test$info1, type = 'l', col = 'blue', ylab = 'Information', xlab = expression(theta), lwd = 2.5, main = 'Subdomain 1')
plot(df.test$theta, df.test$info2, type = 'l', col = 'blue', ylab = 'Information', xlab = expression(theta), lwd = 2.5, main = 'Subdomain 2')



#Find the maximum information:
max.info <- 0
for(it in 1:number.items){
  extr <- extract.item(mod, item = it)
  if(max(iteminfo(extr,Theta = theta.grid, degrees = c(90,0)) > max.info)){ max.info <- max(iteminfo(extr, Theta = theta.grid, degrees = c(90,0)))}
  if(max(iteminfo(extr,Theta = theta.grid, degrees = c(0,90)) > max.info)){ max.info <- max(iteminfo(extr, Theta = theta.grid, degrees = c(0,90)))}
}

max.info 
source("C:/Users/ciaconangelo/Documents/R1 Code Library/multiplot function.R")

for(it in 1:16){
  
  extr <- extract.item(mod, item = it)
  info <- iteminfo(extr, Theta = theta.grid, degrees = c(0, 90))
  df1 <- data.frame('theta' = seq(-3, 3, length.out = 120), 'info'=info)
  
  plot.info <-   ggplot(data = df1, aes(x = theta, y = info)) +
      geom_line() + 
      coord_cartesian(ylim = c(0, max.info), xlim = c(-3, 3)) +
      labs(title = paste0(item.labels[it]), x = expression(theta), y = 'Information') +
      theme(plot.title = element_text(hjust = 0.5)) 
  
  
  trace <- probtrace(extr, Theta = theta.grid)
  df2 <- melt(trace)
  df2$theta <- seq(-3, 3, length.out = 120)
   
  plot.icc <- ggplot(data=df2,
      aes(x=theta, y=value, colour=Var2)) +
      geom_line() +
      coord_cartesian(ylim = c(0,1)) +
      labs(title = paste0(item.labels[it]), x = expression(theta), y = 'Probability', color = 'Category') +
      theme(plot.title = element_text(hjust = 0.5)) +
      theme(legend.position=c(.5, .95), legend.direction = 'horizontal') +
      scale_color_manual(labels = paste0(item.range[, it]), values = paste0(item.range[,it] + 1))  
  
  
  multiplot(plot.info, plot.icc, cols = 2)
  
}



for(it in 1:8){
  extr <- extract.item(mod, item = it)
  info <- iteminfo(extr, Theta = cbind(seq(-3, 3, length.out = 120), 0), degrees = c(0, 90))
  df1 <- data.frame('theta' = seq(-3, 3, length.out = 120), 'info'=info)
  plot.info <-   ggplot(data = df1, aes(x = theta, y = info)) +
    geom_line() + 
    coord_cartesian(ylim = c(0, max.info), xlim = c(-3, 3)) +
    labs(title = paste0(item.labels[it]), x = expression(theta), y = 'Information') +
    theme(plot.title = element_text(hjust = 0.5)) 
  
  
  trace <- probtrace(extr, Theta = cbind(seq(-2, 2, length.out = 120), 0))
  df2 <- melt(trace)
  df2$theta <- seq(-3, 3, length.out = 120)
   plot.icc <- ggplot(data=df2,
                     aes(x=theta, y=value, colour=Var2)) +
    geom_line() +
    coord_cartesian(ylim = c(0,1)) +
    labs(title = paste0(item.labels[it]), x = expression(theta), y = 'Probability', color = 'Category') +
    theme(plot.title = element_text(hjust = 0.5)) +
    theme(legend.position=c(.5, .95), legend.direction = 'horizontal') +
    scale_color_manual(labels = paste0(item.range[, it]), values = paste0(item.range[,it] + 1))  
  
  
  multiplot(plot.info, plot.icc, cols = 2)
  
}



for(it in c(5, 9:16) ){
  extr <- extract.item(mod, item = it)
  info <- iteminfo(extr, Theta = theta.grid, degrees = c(90, 0))
  df1 <- data.frame('theta' = seq(-3, 3, length.out = 120), 'info'=info)
  plot.info <-   ggplot(data = df1, aes(x = theta, y = info)) +
    geom_line() + 
    coord_cartesian(ylim = c(0, max.info), xlim = c(-3, 3)) +
    labs(title = paste0(item.labels[it]), x = expression(theta), y = 'Information') +
    theme(plot.title = element_text(hjust = 0.5)) 
  
  
  trace <- probtrace(extr, Theta = theta.grid)
  df2 <- melt(trace)
  df2$theta <- seq(-3, 3, length.out = 120)
   plot.icc <- ggplot(data=df2,
                     aes(x=theta, y=value, colour=Var2)) +
    geom_line() +
    coord_cartesian(ylim = c(0,1)) +
    labs(title = paste0(item.labels[it]), x = expression(theta), y = 'Probability', color = 'Category') +
    theme(plot.title = element_text(hjust = 0.5)) +
    theme(legend.position=c(.5, .95), legend.direction = 'horizontal') +
    scale_color_manual(labels = paste0(item.range[, it]), values = paste0(item.range[,it] + 1))  
  
  
  multiplot(plot.info, plot.icc, cols = 2)
  
}

```
